---
title: "Sensitivity and Specificity"
author: "Your Name Here"
date: "October 5, 2015"
output: html_document
---


## Readings

***APM***

- ***Chapter 5 Measuring Performance in Regression Models*** (esp. ***5.2 The Variance Bias Trade-Off***)  (5 pages)
- ***Chapter 11 Measuring Performance in Classification Models*** (~20 pages)
- ***Chapter 7.4 K-Nearest Neighbors (regression)*** (2 pages)
- ***Chapter 13.5 K-Nearest Neighbors (classification)*** (3 pages)


```{r, echo=FALSE, results='hide', warning=FALSE }
packs <-  c('ggplot2', 'magrittr', 'dplyr', 'caret', 'AppliedPredictiveModeling')

for( nm in packs ) { 
  # message(nm)
  if( ! nm  %in% installed.packages()[,1]  ) install.packages(nm)
  library(nm, character.only = TRUE)
}

.. = NULL  # For Aesthetics

```


## EXERCISE 1: Resampling

`x` is a random variable. We want to not only know what the `mean(x)` is but want to calculate the uncertainty of `mean(x)`.  Measuring the uncertainty requires repeated measurements of `mean(x)`.

- Calculate the mean of `x`.
- Calculte the `sd( mean(x) )` using the **using 10-fold cross-validation**.  Create your own folds, show your work. (An example is for the Bootstrap is given as a hint. )


```{r}
set.seed(1) 
for (k in 1:10) {
  x <- runif(20,1,20)
}



x_mean = mean(x)

k=10

# CROSS-VALIDATION
# ... YOUR WORK HWEW

x_mean<- numeric()
for(k in 1:10) {
  x_mean <- append( x_mean, sample(x,replace=TRUE) %>% mean)
}
sd_cv <- sd(x_mean)
sd_cv



# BOOTSTRAP (EXAMPLE)
sd_boot <- sapply(1:k, function(i) sample(x,replace=TRUE) %>% mean ) %>% sd
sd_boot



```


- sd_cv   is: `r sd_cv`
- sd_boot is: `r sd_boot`



# Exercise 2: Binomial Metrics

Here's a really simple Model of Versicolor iris based on the **iris** data :

```{r}
set.seed(1)
data(iris)

qplot( data=iris, x=Petal.Length, y=Sepal.Length, color=Species )

# Create Dependent Variable
iris$Versicolor <- 
  ifelse( iris$Species == 'versicolor', "versicolor", "other" ) %>% as.factor
iris$Species = NULL 

wh <- sample.int( nrow(iris), size=nrow(iris)/2 )
train <- iris[ wh,]
test <- iris[ -wh, ]


fit.glm <- glm( Versicolor ~ . - Sepal.Length, data=train, family=binomial )
```


Use the models to and write functions to calculate:

* Prevalence 
* Accuracy
* Error Rate / Misclassification Ratefdsv zfvf th ynjrgtjy dsaSA bvcdcv 
* True Positive Rate  
* False Positive Rate
* True Negative Rate  
* False Negative Rate 
* Sensitivity 
* Specificity 
* Recall 
* Precision

The functions should take two logical vectors of the same length, `y` and `yhat`

```{r}

prevalence = function(y,yhat) {(sum(yhat)+sum(!yhat))/(sum(y)+sum(!y)+sum(yhat)+sum(!yhat))}
accuracy   =  function(y,yhat) {(sum(yhat & y)+sum(!yhat & !y))/(sum(y)+sum(!y))}
error_rate =  function(y,yhat) {(sum(yhat & y)+sum(!yhat & !y))/(sum(y)+sum(!y))}
tpr = function(y,yhat) {(sum(yhat & y))/sum(y)}
fpr =     # See Example
tnr = function(y,yhat) {(sum(!yhat & !y))/(sum(!y))}
sensitivity = function(y,yhat) {(sum(yhat & y))/(sum(y))}
specificity = function(y,yhat) {(sum(!yhat & !y))/(sum(!y))}
recall = function(y,yhat) {(sum(yhat & y))/(sum(y))}
precision = function(y,yhat) {(sum(yhat & y))/(sum(yhat))}

# EXAMPLE: fpr
# The FPR is THE NUMBER OF FALSE POSITIVES / NEGATIVES (TN+FP)

threshold = 0.5 
y = test$Versicolor == 'versicolor'
yhat = predict(fit.glm, test, type="response") > threshold


fpr = function(y,yhat)
  sum(yhat & !y)  / # FP
  sum(! y)                # N

fpr(y,yhat)
##AL: see wikipedia page
prevalence(y,yhat)
accuracy (y,yhat)
error_rate(y,yhat)
tpr (y,yhat)
fpr (y,yhat)
tnr (y,yhat)
sensitivity(y,yhat)
specificity(y,yhat)
recall(y,yhat)
precision (y,yhat)

```

- What is wrong with the modeling approach used?





