---
title: "06-exercises"
author: "Anurag Lal"
date: "2016-05-22"
output: html_document
---

## Reading:
- **APM** Chapter 8.6 and 8.8 
- **APM** Chapter 14.8 
- **APM** Chapter 7.1 & 7.3 "Non-Linear Regression Models"
- **APM** Chapter 13.2 & 13.4 "Non-Linear Classifcation Models"


```{r,echo=FALSE}

packs <-  c('AppliedPredictiveModeling', 'ggplot2', 'magrittr', 'dplyr')

for( nm in packs ) { 
  # message(nm)
  if( ! nm  %in% installed.packages()[,1]  ) install.packages(nm)
  library(nm, character.only = TRUE)
}

# Load data set into environment
data(FuelEconomy)
.. = NULL  # Needed for aesthetics 

FE <- dplyr::bind_rows(cars2010, cars2011, cars2012)    # Define Da

```

## Fuel Economy 


This week we return to the Fuel Economy Data having learned much about model building. This assignment is to go through the process of building several regression models and pick the most predictive model. Use the `FE` data set created for you above.


Start by making choosing a metric and making a naive guess of model performance: 

Metric: _____RMSE__________
Naive Guess: _______MEAN________
Expected Model Performance (based on Naive Guess): _______________

Show your work below for the calculations

```{r, warning=FALSE} 
rmse <- function(y,yhat) {
  ( y - yhat )^2  %>% mean   %>% sqrt 
}
  
naive_guess = mean(cars2010$FE)

err_naive_guess = rmse(cars2010$FE,naive_guess)
err_naive_guess


```


Based only your intuition, how low do your think you can get your metric: __difference between predicted and actual outcome_________


## Examine your data

 * Plot your response/outcome 

 * Make a guess of a strong predictor: ______EngDispl___________  
 * Plot your response vs your predictor. 

```{r, warning=FALSE, message=FALSE}
fit.lm.init<-lm(FE ~ EngDispl,data=cars2010)

yhat <- predict(fit.lm.init,cars2011)
qplot(cars2011$EngDispl,yhat)

```



## Build Simple Models

Using **caret**, build a simple linear model and a simple tree model. 

```{r, warning=FALSE, message=FALSE}
library(caret)

ctrl<-trainControl(method="boot",savePredictions = T)
fit.lm <- train(FE ~ EngDispl,data=cars2011,trControl=ctrl,method="glm")
fit.rp <- train(FE ~ EngDispl,data=cars2011,trControl=ctrl,method="rpart")

```


What did you learn about the data from these models.




## Build More Advanced Models

Now refine your models. Use **caret** to build advanced models:
- one that uses model averaging (bagging) 
- one that uses boosting 

```{r, warning=FALSE, message=FALSE}

# Your work here.
fit.bag   <- train(FE ~ EngDispl,data=cars2011,trControl=ctrl,method="bagEarth")

fit.boost <- train(FE ~ EngDispl,data=cars2011,trControl=ctrl,method="gbm",verbose=F)

```


## Conclusion 

Which model would you use and why?  Under different circumstances why would you choose one of the other models.

fit.boost(boosting using gbm model) is the best one with RMSE 4.5.
Bagging models will be preferred when performance considerations are there, as parallel processing is possible. In Boosting processing is sequential.

